---
title: "Twitter coffee - w2"
author: "Tharindu"
date: "12/08/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

install.packages("rtweet")
install.packages("emo")
install.packages("tidytext")
install.packages("tidyverse")

install.packages("ggplot2")
install.packages("ggraph")
install.packages("igraph")
install.packages("ggmap")

library(tidyverse)
library(rtweet)
library(ggplot2)
library(ggraph)
library(igraph)
library(ggmap)

```

## Data import

Step 1. collect tweets about coffee

```{r}
auth_setup_default()
coffee_tweets<-search_tweets(
  q="BMW",
  n=20000,
  include_rts = FALSE,
  lang="en",
  retryonratelimit = TRUE
)

```

Cleaner version:

```{r}
# #look at first 6 obs
# coffee_tweets%>%
#   head()
# 
# #look at structure
# coffee_tweets%>%
#   str()
# 
# 
# coffee_short<-coffee_tweets%>%
#   select(id, screen_name, created_at, text, favourites_count, retweet_count)
# 
# coffee_short<-coffee_tweets%>%
#   select(id,full_text)


coffee_tweets%>%write_csv("coffee_short_7_10_21.csv")
coffee_tweets<-read_csv("C:/Users/Admin/Documents/R/coffee_short_7_10_21.csv")

```

### Explore frequency of tweets


```{r}
ts_plot(coffee_tweets, "hours") +
  labs(x = NULL, y = NULL,
       title = "Frequency of tweets with coffee",
       subtitle = paste0(format(min(coffee_tweets$created_at), "%d %B %Y"), " to ", format(max(coffee_tweets$created_at),"%d %B %Y")),
       caption = "Coffee tweets Data collected from Twitter") +
  theme_minimal()
```

### Top tweeting location
Most Twitter users turn off their location in their privacy settings but those that don’t add valuable location information to their tweets. We can count unique values of the “place_full_name” variable to obtain the most frequent tweet location.


```{r}
coffee_tweets %>% 
  filter(!is.na(source)) %>% 
  count(source, sort = TRUE) %>% 
  top_n(10)
```

### Most frequently shared link

The `urls_expanded_url` variable provides the full URL of shared links. Here we exclude tweets without a shared link, count, sort the frequency of links in descending order and print the top 5.

```{r}
coffee_tweets %>% 
  filter(!is.na(source)) %>% 
  count(source, sort = TRUE) %>% 
  top_n(5)
```
### Most retweeted tweet

`retweet_count` variable shows retweeting. We sort all the tweets in descending order by the size of the “retweet_count”, slice off the top row and print the date, handle, text and retweet count.

```{r}
coffee_tweets %>% 
  arrange(-retweet_count) %>%
  slice(1) %>% 
  select(created_at, full_text, text, retweet_count)
```

## Embed tweets in the RMarkdown

`gadenbuie/tweetrmd: Embed Tweets in R Markdown`
Easily embed Tweets anywhere R Markdown turns plain text into HTML.

https://github.com/gadenbuie/tweetrmd


```{r}
# #devtools::install_github("gadenbuie/tweetrmd")
# #devtools::install_github('rstudio/webshot2')
# library(tweetrmd)
# tweet_screenshot(tweet_url("Lindt", "823930875213676544"))

```

### Most liked tweet

To find the most liked tweet we can sort our tweets by the “favorite_count” variable in descending order and print the rows with the top 5 highest counts.

```{r}
coffee_tweets %>% 
  arrange(-favorite_count) %>%
  top_n(5, favorite_count) %>% 
  select(created_at, full_text, text, favorite_count)


```

### Top tweeters

To identify the most active tweeters we can use the “screen_name” variable to tot up the number of tweets by Twitter handle. We can then add back the @ symbol using the paste0() function.

```{r}
coffee_tweets %>% 
  count(full_text, sort = TRUE) %>%
  top_n(10) %>%
  mutate(full_text = paste0("@", full_text))
```

## Top emoji

To identify the most frequently used emoji we can use the `ji_extract_all()` function from the `emo` package. 

This function extracts all the emojis from the text of each tweet. 

We can then use the unnest() function from the tidyr package to split out the emojis, count, sort in descending order and identify the top 10.

```{r}
# #devtools::install_github("hadley/emo")
# library(emo)
# coffee_tweets %>%
#   mutate(emoji = ji_extract_all(text)) %>%
#   unnest(cols = c(emoji)) %>%
#   count(emoji, sort = TRUE) %>%
#   top_n(10)
```


### Top hashtags

To pull out the hashtags from the text of each tweet we first need to convert the text into a one word per row format using the `unnest_tokens()` function from the `tidytext` package. 
We then select only those terms that have a hashtag, count them, sort in descending order and pick the top 10.
```{r}
# library(tidytext)
# coffee_tweets %>% 
#   unnest_tokens(hashtag, text, "tweets", to_lower = FALSE) %>%
#   filter(str_detect(hashtag, "^#"),
#         hashtag != "#ClimateEmergency") %>%
#   count(hashtag, sort = TRUE) %>%
#   top_n(10)
```

### Top mentions

Here we tokenise the text of each tweet and use `str_detect()` from the `tidyverse` package to filter out words that start with an @ .
```{r}
# coffee_tweets %>% 
#   unnest_tokens(mentions, text, "tweets", to_lower = FALSE) %>%
#   filter(str_detect(mentions, "^@")) %>%  
#   count(mentions, sort = TRUE) %>%
#   top_n(10)
```